\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-08-17 NAR_DRAFT.tex
check in change

\subsection{Real Data}
We analyzed two real data sets, one from an acute myeloid leukemia, and one from a multi-region sequencing experiment in breast cancer \cite{Griffith2015,Shi2018}.
We downloaded the normal and primary tumor bam files generated for the whole genome sequences in \citet{Griffith2015} from dbGaP accession number phs000159.v8.p4.
\citet{Griffith2015} generated a platinum set of variant calls for this primary tumor, which we obtained from supplementary materials, and used for our true positive dataset.
The whole exome sequencing bam files generated by \citet{Shi2018} were downloaded from NCBI SRA no. SRP070662.
\citet{Shi2018} generated a gold set of variant calls for each tumor region sequenced, which we obtained from supplementary materials and used for our true positive dataset.
We called variants using Mutect 1.1.7 with the same parameters as described above, except that both of these data sets were originally aligned to GRCH37, and we used that reference here.

@@

	We use the Integrated Calibration Index to quantify the difference between MuTect and the Calibrated model \cite{Austin2019}.
	Briefly, a loess-smoothed regression is fit by regressing the binary (T/F) variant classification against the reported posterior probability of a true variant for both MuTect and the Calibrated model (Figure \ref{NAR-wes_fig} \textbf{e}).
	Plotting the smoothed regression predictions against the actual predictions would result in a diagonal line, and the Integrated Calibration Index is the average distance between the loess fit and a diagonal line.

@@

The \batcave algorithm focuses on the tri-nucleotide context and substitution type. 
There are many other types of \textit{genomic context} which can effect local mutation rates \cite{Buisson2019}.
These could be very useful in computing a local or regional mutation rate, as opposed to the genome-wide but tumor-specific mutation rate used by \batcave.

@@

\bibliography{caller_paper}

@@

\begin{table*}[b]
  \tableparts{%
  \caption{This is a table with $\mu$, auroc, auprc, ICI, and maybe fraction called?}
  \label{table:01}%
  }{%
  \begin{tabular*}{\textwidth}{@{}lllllllll@{}}
  \toprule
  Depth & Mutation profile & $\mu$ & AUROC & & AUPRC & & ICI & 
  \\
  & & (estimated) & MuTect & \batcave & MuTect & \batcave & MuTect & \batcave
  \\
  \colrule
  100X whole genome & Concentrated & 3.6e-7 & .987 & .993 & .972 & .975 & -- & --
  \\
  100X whole genome & Intermediate & 3.2e-7 & .987 & .989 & .972 & .973 & -- & --
  \\
  100X whole genome & Diffuse & 3.2e-7 & .988 & .989 & .971 & .973 & -- & --
  \\
  500X whole exome & Concentrated & 3.6e-7 & .848 & .929 & .674 & .758 & .138 & .109
  \\
  500X whole exome & Intermediate & 3.6e-7 & .847 & .881 & .677 & .706 & .108 & .112 
  \\
  500X whole exome & Diffuse & 3.6e-7 & .850 & .873 & .676 & .698 & .105 & .116
  \\
  \citet{Williams2016} & Actual & 3.6e-8 & -- & -- & .995 & .996 & -- & --
  \\
  \citet{Shi2018} & Actual & 3.6e-8 & -- & -- & .972 & .972 & -- & --
  \\
  \botrule
  \end{tabular*}%
  }
  {$\mu$ = per-base mutation rate, AUROC/AUPRC = area under ROC/PRC curve, ICI = Integrated calibration index.}
  \end{table*}
\end{document}

>>>>

\subsection{Real Data}
\begin{itemize}
  \item aml31 \cite{Griffith2015}
  \item item used only the platinum calls for evaluation
  \item Shi2018 \cite{Shi2018}
  \item used the gold standard calls, and combined all six biological replicates 
\end{itemize}

@@

	We use the Integrated Calibration Index to quantify the difference between MuTect and the Calibrated model \cite{Austin2019}.
	Briefly, a loess-smoothed regression is fit by regressing the binary (T/F) variant classification against the reported posterior probability of a true variant for both MuTect and the Calibrated model (Figure \ref{NAR-wes_fig} \textbf{e}).
	Plotting the smoothed regression predictions against the actual predictions would result in a diagonal line, and the Integrated Calibration Index is the average area between the loess fit and a diagonal line.

@@

The \batcave algorithm focuses on the tri-nucleotide context and substitution type, but there are many other types of \textit{genomic context} which can effect local mutation rates \cite{Buisson2019}.
These other types of context could be very useful in computing a local or regional mutation rate, as opposed to the genome-wide but tumor-specific mutation rate used by \batcave.

@@

@@

\section{Supplememtary Table}

\begin{table*}[b]
  \tableparts{%
  \caption{This is a table with $\mu$, auroc, auprc, ICI, and maybe fraction called?}
  \label{table:01}%
  }{%
  \begin{tabular*}{\textwidth}{@{}lllllllll@{}}
  \toprule
  Depth & Mutation profile & $\mu$ & AUROC & & AUPRC & & ICI & 
  \\
  & & (estimated) & MuTect & \batcave & MuTect & \batcave & MuTect & \batcave
  \\
  \colrule
  100X whole genome & Concentrated & 3.6e-7 & .987 & .993 & .972 & .975 & -- & --
  \\
  100X whole genome & Intermediate & 3.2e-7 & .987 & .989 & .972 & .973 & -- & --
  \\
  100X whole genome & Diffuse & 3.2e-7 & .988 & .989 & .971 & .973 & -- & --
  \\
  500X whole exome & Concentrated & 3.6e-7 & .848 & .929 & .674 & .758 & .138 & .109
  \\
  500X whole exome & Intermediate & 3.6e-7 & .847 & .881 & .677 & .706 & .108 & .112 
  \\
  500X whole exome & Diffuse & 3.6e-7 & .850 & .873 & .676 & .698 & .105 & .116
  \\
  \citet{Williams2016} & Actual & 3.6e-8 & -- & -- & .995 & .996 & -- & --
  \\
  \citet{Shi2018} & Actual & 3.6e-8 & -- & -- & .972 & .972 & -- & --
  \\
  \botrule
  \end{tabular*}%
  }
  {$\mu$ = per-base mutation rate, AUROC/AUPRC = area under ROC/PRC curve, ICI = Integrated calibration index.}
  \end{table*}

  \bibliography{caller_paper}
\end{document}
